Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
cdrp

\todo{metion CIFAR-5}
\subsection{CDRP Model Assembly}
Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5 and their relationship to the CDRP clusters by encoding samples using all CDRP models.
Instead of using Venn diagram like the intro example in Figure~\ref{fig:assemble-example-venn}, we use the network diagram in Figure~\ref{fig:network-venn} to represent the relationship between subclasses and clusters.

>>>>

%\todo{metion CIFAR-5}
\subsection{CDRP Model Assembly}
Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5	\footnote{CIFAR-5 is a shorthand refering to samples having the first 5 class labels in CIFAR-100.} and their relationship to the CDRP clusters by encoding samples using all CDRP models.
Instead of using Venn diagram like the intro example in Figure~\ref{fig:assemble-example-venn}, we use the network diagram in Figure~\ref{fig:network-venn} to represent the relationship between subclasses and clusters.
